---
title: "stats"
author: "Monique Sierra"
date: "11/7/2020"
output: html_document
---
Find a multivariable linear regression model to predict the number of infections  per million population( y)as a function of the following independent variables:
Four Continuous9 and ordinal) variables :Population density ( population divided by area of a country), wealth as measured by Gross national Income (GNI per capita),  mean or median age of the population, ranking of healthcare system,  and two /binary variables ( assign 1 or 0): system of government (democratic or authoritarian) and  geography of a country (island or not). You need to conduct a complete analysis, specifically graph the histogram of the continuous variables( normal or at least symmetric is good). Graph y versus each continuous variable to see if there is a correlation, look at the p-values to see the significance of each variable, find correlation coefficients between pairs of continuous variables to get rid of redundant variables.
Repeat  the regression as (a) but this time use number of death per million population as your dependent variable. 
 Pick a couple of countries( preferably other than countries in your sample) and determine a 95% prediction interval for the number of infections and number of death. Does the actual value falls in this interval?  
Add something of your own to the project which involves some other statistical analysis involving the same data. This may involve a parametric or non-parametric methods you learned in this course or something of your own finding . 
State your conclusions. Specifically look at the sign and size of the  coefficients of regression equations you found in (a0 and (b). What do those coefficients tell us?
```{r }

require(ggiraph)
require(ggiraphExtra)
require(ggplot2)

COVID_STATSforR <- read.csv(file.choose(), header = T)
attach(COVID_STATSforR)
head(COVID_STATSforR$geo)
covid <-COVID_STATSforR

summary(covid$geo)
head(covid$geo)

```
Find a multivariable linear regression model to predict the number of infections per million population( y)as a function of the following independent variables:
Four Continuous9 and ordinal) variable

```{r}

library(moonBook)
heyyy = lm(pop ~ age,data=covid)
summary(heyyy)
plot(heyyy)




```

```{r}
require(ggplot2)

inf.age <- lm(infect ~ age, data = covid)
summary(inf.age)
ggplot(covid,aes(y=infect,x=age))+geom_point()+geom_smooth(method="lm")

```

```{r}
library(ggformula)
library(ggeffects)
library(moonBook)



ggpredict(fit4,interactive=TRUE)



```
```{r}
library(ggplot2)
library(ggformula)

ggplot(data = covid,
       mapping = aes(x = infect, y = age)) +
  geom_point()

head(covid$geo)
covid$geo <-as.factor(covid$geo)
covid$gov <-as.factor(covid$gov)

levels(covid$gov) <-c('Dem','Auth')
table(covid$gov)

covid$geo <-levels(c("Isle","Cont"))
covid$gov <-levels(c("Dem","Auth"))
str(covid$gov)



wealth.age <- lm(death ~ wealth, data = covid)
plot(wealth.age)


gf_point(deaths ~ wealth, data = covid, color =~gov, size = ~geo)



```



Interaction (?) infection w age * geo
```{r}
library(HistogramTools)
require(ggeffects)

fit4=lm(infect ~ age*geo,data=covid)
summary(fit4)

plot(fit4)


hist.age <- hist(covid$age)
hist.wealth <- hist(covid$wealth)

PlotRelativeFrequency(hist.age, main = "age wealth", col = c1, ylim=c(0,.6), xlim=c(0,60000))
PlotRelativeFrequency(hist.wealth, col = c2, add = TRUE)


```


Age
```{r}

heyo <- lm(infect ~age, data = covid)
summary(heyo)
plot(heyo)
plot(heyo$fitted, heyo$residuals, xlab = "Fitted Values", ylab = "Residuals")
abline(0,0)

```

random hist death v infections
```{r}

library(HistogramTools)

mycol <- rgb(0, 0, 255, max = 255, alpha = 125, names = "pink50")
mycol <- rgb(0, 0, 255, max = 255, alpha = 125, names = "blue50")
c1 <- rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue")
c2 <- rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink")

hist.pop <- hist(covid$death, col = c1)
hist.inf <- hist(covid$infect)

PlotRelativeFrequency(hist.pop, main = "death v infections", col = c1, ylim=c(0,.55), xlim=c(0,45000))
PlotRelativeFrequency(hist.inf, col = c2, add = TRUE)
                 

```

```{r}




```
