---
title: "Exam 1"
author: "Monique Sierra"
date: "9/16/2020"
output: html_document
---


```{r setup, include=FALSE}
library(lubridate)
library(readxl)
Student.Data <- read.csv("~/Downloads/Student.Data.csv")
summary(Student.Data)

backup <-Student.Data$birth_dte
Student.Data$birth_dte <- backup

head(Student.Data$birth_dte)
```

### 1. summary of age

```{r} 

Student.Data$birth_dte<-mdy(as.character(Student.Data$birth_dte, rm.na= TRUE))

summary(round(as.duration(Student.Data$birth_dte %--% "2009-09-15")/dyears(1),1))


```
##### We see the average age of students in 2009 was 17 years old, with the youngest being a mere 13 and the oldest at 35.

### 2. age boxplot sept 2009

```{r}

boxplot(round(as.duration(Student.Data$birth_dte %--% "2009-09-15")/dyears(1),1), ylab = 'age', col = "turquoise")

```

##### The four outliers are apparent. We have a good visual of the majority falling between 13 and 22.

### 3. significant difference of ages in males and females

```{r}

student.ages <-as.duration(Student.Data$birth_dte %--% "2009-09-15")/dyears(1)
           

t.test(student.ages ~ as.factor(Student.Data$gender), alternative = "two.sided")


```

##### The average age of females was 17 while that of men was 17.15. With alpha as .05, the p-value was slightly lower. This results in the rejection of the null which says the difference of their means is 0.

### 4. five most popular majors

```{r}

TabMaj <-table(Student.Data$major_1)
TabMaj[head(order(-TabMaj),(5))]


```
##### The five most popular majors are Business, Kinesiology, Undeclared, Biology, and Multidisciplinary Studies.

### 5. males v females in most popular major
```{r}

table(Student.Data$major_1 == 'BUSI', Student.Data$gender)

```
##### There appears to be 62 women and 105 men studying business, the most popular major. 

### 6. most pop major gpa of men v women sig dif
```{r}
business.gpa <- as.numeric(Student.Data$gpa,Student.Data$major == 'BUSI')

t.test(business.gpa ~ as.factor(Student.Data$gender), alternative = "two.sided")

```
##### It appears that the average gpa of women in business is 2.92, while that of men in business is 2.48. Because the p-value was below alpha, we reject the null and support the alt hypothesis that they are significantly different.

### 7. majors in decreasing order of gpa
```{r}
majors.gpa <-tapply(Student.Data$gpa,Student.Data$major_1, mean)

l.to.small <-order(majors.gpa)


gpa.major <- tapply(Student.Data$gpa,Student.Data$major_1,mean) 
l.to.small <- order(-gpa.major)                
gpa.major[l.to.small]


```
##### The major with the highest gpa appears to be accounting, and the lowest gpa as sociolgy.

### 8. boxplot of term hours earned

```{r}
boxplot(Student.Data$trm_hrs_earned, ylab = 'hours earned', col = "turquoise")

```

##### There appears to be a significant number of outliers that fall below the first quartile. The majority of students are around 13 to 15 hours, with only a small amount going over 15.

### 9. sig dif term hrs earned v hrs attempted
```{r}
t.test(Student.Data$trm_hrs_attempt,Student.Data$local_hrs_earned)

```
##### We see the difference of hours attempted and hours earned has a p-value much smaller than 0. Because of this we reject the null and support the alternative which states that the difference in means is not equal.

### 10. HS gpa men and women

```{r}

mean(Student.Data[Student.Data$gender == 'F', 'HS.gpa'])
mean(Student.Data[Student.Data$gender == 'M', 'HS.gpa'])

```

##### The average GPA of men is 3.25, while the GPA of women is about 3.47. The girls have a slightly higher GPA, but overall the averages appear pretty high. 